\begin{acknowledgements}
\addchaptertocentry{\acknowledgementname} % Add the acknowledgements to the table of contents
I am profoundly grateful to everyone who has provide me assistance and support 
throughout these years to achieve the completion of my master thesis.\\

First of all, my deepest appreciation extends to Prof. Matsui and Prof. 
Yamada from Yokohama National University. The opportunity to collaborate with you on this project has 
been invaluable, and your unwavering guidance and support, both in Japan and Germany despite the 
distance, have been instrumental to my success.
I would also like to thank my supervisor, Rasul Abdulsalamov, whose effective supervision,
motivational encouragement, and consistent cooperation have been essential from start to the finish.

Likewise, I am equally indebted to my colleagues at YNU, particularly Yuta Mori, Chikako Natsumeda, and Yuuki Fukutani, 
whose full cooperation and support, even in the face of language barriers. I am deeply appreciative of their hard work and dedication.\\

My heartfelt thanks go to my husband, Stephan Stahlmann. His constant presence, emotional support, 
and encouragement on every step towards my goal meant everything to me.

I am also grateful to my parents, Ciro Pinedo and Nora Oruna, and my sister, Nathaly Pinedo, 
for their unwavering support from Peru and for always believing in me. 
Furthermore, I would like to thank my host parents, Karin and Ivano Rinaldo, and my 
extended family, the Stahlmann family. Their wishes for my success and comfort during challenging times have been
a source of strength.\\

Lastly, I would like to mention my friends: Johanna Müller, Andrea Toledo, Azusa Soejima, Dominik Horn,
Lisa Kahler, Andrés Splendido, Josefine Dannenberg and Alonso López.
Their assistance, time and kindness during the course of this
thesis have been a tremendous help.\\

Muchas gracias a todos.

\end{acknowledgements}
